\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-02-14 manuscript.Rnw
Update manuscript.Rnw
Increase number of PSA iterations and use bootstrap for partitioned survival model

Decisions informed by economic models and CEA are subject to uncertainty. One source of decision uncertainty stems from uncertainty in the underlying model parameters. Parameter uncertainty is typically quantified using probabilistic sensitivity analysis (PSA), which involves randomly sampling the model parameters from suitable probability distribution and simulating the model for each sampled parameter set \citep{claxton2005probabilistic}. When combined with individual-level simulation, PSA can take an appreciable amount of time to run \citep{ohagan2007monte}.

@@

\subsection{Cohort discrete time state transition models} \label{sec:cDTSTMs}
cDTSTMs simulate the probability that a cohort of patients is in each of $H$ health states over time. Time is partitioned into intervals $\{[0, t_1), [t_1, t_2), \ldots, [t_C, t_{C+1})\}$ with each interval $0,\ldots, C$ reffered to as a model cycle. We denote $t_c$ as the time at the start of model cycle $c$. An $H \times 1$ state vector that stores the probability of being in each health state at cycle $c$ is written as $x_c = (x_{1c}, x_{2c}, \ldots, x_{Hc})$ where $\sum_h x_{hc} = 1$. A transition probability matrix is an $H \times H$ matrix denoted by $P_c$ where the $(r,s)$th element represents a transition from state $r$ to state $s$ between model cycles $c$ and $c+1$. The state vector at cycle $c+1$ for each of $C$ model cycles is given by,

@@

<<ictstm_n_samples>>=
n_samples <- 100
@

@@

<<psm_survmods_params>>=
survmods_params <- create_params(psmfit_soc_wei, n = n_samples, 
                                 uncertainty = "normal")
survmods_params$pfs$coefs$scale <- cbind(survmods_params$pfs$coefs$scale,
                                         coef_pfs_wei)
survmods_params$os$coefs$scale <- cbind(survmods_params$os$coefs$scale,
                                        coef_os_wei)
survmods_params$pfs$coefs$scale[1:2, ]
@

>>>>

Decisions informed by economic models and CEA are subject to uncertainty. One source of decision uncertainty stems from uncertainty in the underlying model parameters. Parameter uncertainty is typically quantified using probabilistic sensitivity analysis (PSA), which involves randomly sampling the model parameters from suitable probability distributions and simulating the model for each sampled parameter set \citep{claxton2005probabilistic}. When combined with individual-level simulation, PSA can take an appreciable amount of time to run \citep{ohagan2007monte}.

@@

\subsection{Cohort discrete time state transition models} \label{sec:cDTSTMs}
cDTSTMs simulate the probability that a cohort of patients is in each of $H$ health states over time. Time is partitioned into intervals $\{[0, t_1), [t_1, t_2), \ldots, [t_C, t_{C+1})\}$ with each interval $0,\ldots, C$ referred to as a model cycle. We denote $t_c$ as the time at the start of model cycle $c$. An $H \times 1$ state vector that stores the probability of being in each health state at cycle $c$ is written as $x_c = (x_{1c}, x_{2c}, \ldots, x_{Hc})$ where $\sum_h x_{hc} = 1$. A transition probability matrix is an $H \times H$ matrix denoted by $P_c$ where the $(r,s)$th element represents a transition from state $r$ to state $s$ between model cycles $c$ and $c+1$. The state vector at cycle $c+1$ for each of $C$ model cycles is given by,

@@

<<ictstm_n_samples>>=
n_samples <- 1000
@

@@

<<psm_survmods_params, warning = FALSE>>=
survmods_params <- create_params(psmfit_soc_wei, n = n_samples, 
                                 uncertainty = "bootstrap", 
                                 max_errors = 5, silent = TRUE)
survmods_params$pfs$coefs$scale <- cbind(survmods_params$pfs$coefs$scale,
                                         coef_pfs_wei)
survmods_params$os$coefs$scale <- cbind(survmods_params$os$coefs$scale,
                                        coef_os_wei)
survmods_params$pfs$coefs$scale[1:2, ]
@
